### 2021-04-28 manuscript.Rmd
added modified SPRT

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(citr)

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(citr)
library(MSPRT)

@@

"From a practical perspective, there are many hypothesis testing contexts where it is not feasible to implement a SPRT. For instance, a SPRT cannot be applied when data are not collected sequentially. Similarly, it cannot be applied when it is not possible to perform the evaluation as soon as participants are treated... To address these challenges, group sequential designs have been developed to allow for the evaluation of patient outcomes only after groups of patients have been observed or at scheduled interim analysis times" [@pramanik2021: p. 4-5]

# To add

In this paper, the example we use looks at the performance of these procedures under ideal conditions (an oracle prior setup), i.e. the performance of these procedures when the true effect size matches the model expectations as closely as possible: the population effect size is either equal to zero or it matches the effect size parameter (SPRT, Fixed, GS-designs) or the mode of the prior distribution on effect size (SBF) in the alternative model [@stefan2020: p. 15].
